\documentclass[11pt]{article}
\usepackage{enumerate}
\usepackage[bottom=0.8in,top=0.2in]{geometry}
\newcommand\tab[1][1cm]{\hspace*{#1}}

\title{\begin{Huge}
\date{}
\textbf{PROJECT SYNOPSIS}
\end{Huge}}
\begin{document}
\maketitle

\begin{enumerate}
\item TITLE OF THE PROJECT: Application For Managing Veterinary Polyclinic
\item AREA OF THE PROJECT: Database Management System
\item PROJECT TEAM MEMBERS DETAILS: GROUP NO. 42 \\



\begin{tabular}{|c|c|c|c|}
\hline NAME & ROLL NO. & EMAIL & CONTACT \\ \hline
Shalini Prasanna & 4452 & shalini.prasanna@cumminscollege.in & 9923124646 \\ \hline
T. Pavithra & 4473 & t.pavithra@cumminscollege.in & 9960822880\\ \hline
Supriya Waghmare & 4482 & supriya.waghmare@cumminscollege.in & 7028291278\\ \hline
Ashlesha Waikos & 4483 & ashlesha.waikos@cumminscollege.in & 9764486484 \\ \hline
\end{tabular} \\





\item SPONSORING COMPANY DETAILS: Not Available
\item DETAILS OF EXTERNAL GUIDE: Not Available
\item INTERNAL GUIDE: Mrs. Pranjali Deshpande
\item MOTIVATION OF THE PROJECT:
\begin{enumerate}[(i)]
\item To automate the manually maintained record process.
\item Limitations in the currently used handwritten system.
\end{enumerate}
\item SCOPE OF THE PROJECT AND WHAT IS NOT IN SCOPE:
\begin{enumerate}[(i)]
\item This system is limited to only one hospital.
\item Inventory for medicines is not included.
\end{enumerate}
\item EXTERNAL INTERFACES/ TOOLS/ LIBRARIES PLANNING TO USE: \\
JDBC , Java AWT library , Servlet



\item MODULE-WISE DESCRIPTION:
\begin{enumerate}[(I)]
\item Doctor's Login:
\begin{enumerate}[1.]
\item A login page for authorization.
\item Input details compared with the saved staff record.
\end{enumerate}
\item Registration Module:
\begin{enumerate}[1.]
\item For registering new client details.
\item Client details saved in a database.
\end{enumerate}
\item Departments/Inventory module:
\begin{enumerate}[1.]
\item Mysql database for every department.
\item Records can be viewed,updated and deleted across all departments.
\item Inventory details are maintained in a separate database table.
\end{enumerate}
\item Report Generation/Statistics:
\begin{enumerate}[1.]
\item Final reports generated.
\item Statistical data viewed.

\end{enumerate}
\end{enumerate}
\item HARDWARE REQUIREMENTS:
\begin{enumerate}[(i)]
\item Processor: Intel Core i3
\item OS Type: 64 bit
\item RAM: 4 GB

\end{enumerate}
\item SOFTWARE REQUIREMENTS:
Netbeans IDE, Apache Tomcat, Mysql DBMS

\item ANY FUTURE ENHANCEMENTS:
\begin{enumerate}[(i)]
\item A mobile application can be developed.
\item An inventory for medicines can be added.
\item An additional functionality for patient registration could be added.
\end{enumerate}

\end{enumerate} 


\vspace{50mm}
MR. M. P. DEORE   \tab[2cm]     Ms. M. A KAMLAKAR \\
\tab[3cm] (Project co-ordinators)
\end{document}
